figures and calculations for global fisheries management

### 2019-01-12 documents/figs-and-calcs.Rmd
saving figures to folder in documents/figures

#projection_data_fig3$CatchShare <- as.factor(projection_data_fig3$CatchShare)

>>>>

#seperate out with and without catch sahre and then calcualte geo median
#download either geo_median or Gmedian once updated computer
median_math <- projection_data_fig3 %>%
  ungroup() %>%
  select(BvBmsy,FvFmsy, CatchShare) %>%
 group_by(CatchShare) %>%
    na.omit() %>%
    summarize( y=median(BvBmsy,FvFmsy))
